---
title: "Map Of Horrors"
author: "Al Richardson"
output: html_document
---

```{r setup, include=F, message=F}
knitr::opts_chunk$set(echo = TRUE)
```
<hr/>
##### Begun: 2023-02-10
##### Knitted: `r Sys.Date()`
<hr/>
This is a map locating a few locations (all but one, fictional) in which some classic horror stories take place. At this point the locations are:

* Arkham, Massachusetts, USA (from H.P. Lovecraft)
* Miskatonic University, USA, in Arkham, Massachusetts (from H.P. Lovecraft)
* Dunwich, Massachusetts, USA (from H.P. Lovecraft)
* Innsmouth, Massachusetts, USA (from H.P. Lovecraft)
* The Mountains Of Madness, Antarctica (from H.P. Lovecraft)
* Jerusalem's Lot, Maine, USA (from Stephen King)
* The Amityville House, Amityville, New York, USA, Massachusetts (from a real event, and subsequent fictional novel by J. Anson)

```{r map, echo=F, warning=F, message=F}
library(leaflet)

mLocations <- data.frame(name = c("Arkham, MA", "Miskatonic University, Arkham, MA", 
                                  "Dunwich, MA", "Innsmouth, MA", 
                                  "Boundary Of The Mountains Of Madness",
                                  "Boundary Of The Mountains Of Madness",
                                  "Jerusalem\'s Lot, ME", 
                                  "The Amityville Horror House, Amityville, NY"),
                        stories = c(12, 10, 1, 4, 10, 10, 10, 15),
                        lat = c(42.5839, 42.5894, 42.6903, 42.7052, -70.0, 
                                -77.0, 45.9235, 40.6667),
                        lng = c(-70.8389, -70.8211, -71.4574, -70.8057, 100.0, 
                                70.0, -69.5799, -73.4148))

mL <- mLocations %>% 
  leaflet() %>% 
  addTiles() %>%
  addMarkers(lat = mLocations$lat, lng = mLocations$lng) %>%
  addCircles(weight = 1, radius = mLocations$stories * 300) %>% 
  setView(lat = 43.0, lng = -70.0, zoom = 7)

mL

```
