---
title: "Developing Data Products Fractal Visualiser"
author: "Al Richardson"
date: "2023-03-04"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{css, echo=FALSE}
.Kronecker {
  background-color: lightgrey;
  border: 1px solid black;
  font-size: 18px;
  line-height: 23px;
  width: 800px;
  margin-left: 50px;
  margin-bottom: 50px;
}
```

## Introduction
```{css}
slides > slide {
  background: linear-gradient(#ffffff, #ffffff 85%, #ffffff);
  background-color: white;
  }
```
The Shiny application allows one to view a selection of fractal images. The selection of fractals is not even close to being exhaustive.<br><br><br><br><br><br>

<div style='padding:0.1em; background-color:#cdddf4'><span style='font-size:75%'>
  <p style='margin-top:1em; text-align:center'>
    <b><u>Useful References</u></b>
  </p>
  <p style='margin-left:1em;'>
    An introduction to fractals can be found in$^{[1]}$. The code that calculates and plots the fractals here is modified from$^{[2]}$.

  1.  [Fractal](https://en.wikipedia.org/wiki/Fractal), Wikipedia, the free encyclopedia
  2.  [A Few Approaches to Generating Fractal Images in R](https://www.codeproject.com/Articles/1195034/A-Few-Approaches-to-Generating-Fractal-Images-in-R), A. E. Voevudko, Code Project
  </p>
</span></div>

## Interface
Fractals of two types are identified by the way they are generated:

1.  Iterated Function Systems (IFS)
2.  Kronecker Products of Matrices (KP)

The user can select between IFS and KP types and then select a specific example of the chosen type from a drop down list.<br><br><br>

<div style='padding:0.1em; background-color:#f4cdd3'>
<span style='font-size:75%'>
<p style='margin-top:1em; margin-left:1em; text-align:left'>
<b><u>Note:</u></b></p>
<p style='margin-left:1em;'>
    The generation of some famous fractals, such as the Mandelbrot set and the Julia set, are significantly more resource intensive, and are not included here.
</p></span></div>

## Simplified Algorithm
```{r class.source="Kronecker", echo = TRUE}

f = matrix(c(0,1,0, 
             1,1,1, 
             0,1,0), nrow = 3, ncol = 3)
  
mat <- f
for(i in 1:3) mat <- mat%x%f

m = nrow(mat) 
d = 0
X=NULL 
Y=NULL
  
for (i in 1:m) {
  for (j in 1:m) {
    if(mat[i,j]==0) next 
    else {
      d=d+1 
      X[d]=i 
      Y[d]=j 
    } 
  }
}
```
## A Simple KP-Type Fractal
```{r, fig.width=6, fig.height=6, fig.align='center'}
plot(X,Y, pch=3, col = "blue", axes=FALSE, xlab="", ylab="", cex=1.0)
box(col="black")
```



