---
title: "Developing Data Products Fractal Visualiser"
author: "Al Richardson"
date: "2023-03-04"
output: ioslides_presentation
theme: NULL
extra_dependencies: ["float"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{css, echo=FALSE}
.Kronecker {
  background-color: lightgrey;
  font-size: 18px;
  line-height: 23px;
  width: 800px;
  margin-left: 50px;
  margin-bottom: 50px;
}

slides >slide.current{
  background: #e2ded3 !important;
}

```

## Introduction

The Shiny application allows one to view a selection of fractal images. The selection of fractals is not even close to being exhaustive.<br><br><br><br><br><br>

<div style='padding:0.1em; background-color:#cdddf4'><span style='font-size:75%'>
  <p style='margin-top:1em; text-align:center'>
    <b><u>Useful References</u></b>
  </p>
  <p style='margin-left:1em;'>
    An introduction to fractals can be found in$^{[1]}$. The code that calculates and plots the fractals here is modified from$^{[2]}$.

  1.  [Fractal](https://en.wikipedia.org/wiki/Fractal), Wikipedia, the free encyclopedia
  2.  [A Few Approaches to Generating Fractal Images in R](https://www.codeproject.com/Articles/1195034/A-Few-Approaches-to-Generating-Fractal-Images-in-R), A. E. Voevudko, Code Project
  </p>
</span></div>

## Interface
Fractals of two types are identified by the way they are generated:

1.  Iterated Function Systems (IFS)
2.  Kronecker Products of Matrices (KP)

The user can select between IFS and KP types and then select a specific example of the chosen type from a drop down list.<br><br><br>

<div style='padding:0.1em; background-color:#f4cdd3'>
<span style='font-size:75%'>
<p style='margin-top:1em; margin-left:1em; text-align:left'>
<b><u>Note:</u></b></p>
<p style='margin-left:1em;'>
    The generation of some famous fractals, such as the Mandelbrot set and the Julia set, are significantly more resource intensive, and are not included here.
</p></span></div>

## Example Simplified Algorithm

```{r class.source="Kronecker", echo = TRUE}

f = matrix(c(1,0,1, 
             0,1,0, 
             1,0,1), nrow = 3, ncol = 3)

mat <- f
for(i in 1:3) mat <- mat%x%f

m = nrow(mat) 
d = 0
X=NULL 
Y=NULL
  
for (i in 1:m) {
  for (j in 1:m) {
    if(mat[i,j]==0) next 
    else {
      d=d+1 
      X[d]=i; Y[d]=j 
    } 
  }
}
```

---
```{css}
#figr{
  margin-top: -40px !important;
  margin-left: -15px !important;
}
```

<div id = "figr">
```{r , fig.width=7, fig.height=7, fig.align='center'}
par(bg = "#e2ded3")
plot(x = X, y = Y, pch=3, col = "blue", axes=FALSE, cex=1.0, 
     xlab="", ylab="", main = 'Example KP Fractal', cex.main = 3)

```
</div>
